Adaptive Distance Metric Selection for Supervised Classification

### 2016-10-19 latex/Adaptive_distance_metric_notes.tex
Add aims projest

\usepackage{algorithmic}
\usepackage{algorithm}
\usepackage[usenames,dvipsnames]{color}
\usepackage{fullpage,graphicx,amssymb,amsmath}
\usepackage{enumerate}
\usepackage{subfigure}

@@

TODO: Modify to incorporate assumption that $0 \leq d_{ij} \leq 1$ for all $i$ and $j$.

@@

>>>>

\usepackage{algorithmic}
\usepackage{algorithm}
%\usepackage[usenames,dvipsnames]{color}

\usepackage{todonotes}

\usepackage{fullpage,graphicx,amssymb,amsmath}
\usepackage{enumerate}
\usepackage{subfigure}

@@

\todo[inline]{Modify to incorporate assumption that $0 \leq d_{ij} \leq 1$ for all $i$ and $j$.}

\subsection{Similar to previous but we will have just one lambda}
\label{sec:mimax_oneLamnda}
\todo[inline]{FInish this soon and compare with previous approach}

@@

\newpage 
\part{Progress Reports}

\subsection{2016-10-21}
\begin{itemize}
\item Loading instance works

\item Solving  \eqref{model:epsilon_lp_1} works now

\item Model \eqref{model:milp_with_outlier_detection}
works

show some pictures here

\item I did this and that
\end{itemize}
{\bf problems and questions:}
\begin{itemize}
\item queston 1
\item question 2

\end{itemize}
{\bf suggestions:}
\begin{itemize}
\item section \ref{sec:mimax_oneLamnda}
\end{itemize}

\newpage
\part{Tasks to do }

\begin{itemize}
\item put here the ideas from excel
\end{itemize}
